Composable Generalized Consensus

### 2016-01-01 paper/abstract3.tex
A new Isabelle formalization

We present a framework that enables building SMR algorithms out of independent modules. A module is an SMR algorithm that can abort its execution and pass the baton to a new module, allowing a composite SMR algorithm to dynamically switch between modules. 
Crucially, each module can be proved correct once and for all in isolation and our composition theorem guarantees that 
the composition of any number of correct modules is a correct SMR algorithm.

>>>>

We present a framework that enables building SMR algorithms out of independent modules. A module is an SMR algorithm that can abort its execution and pass the baton to a new module, allowing to build composite SMR algorithms which can dynamically switch between modules. 
Crucially, each module can be proved correct once and for all in isolation and our composition theorem guarantees that 
the composition of any number of correct modules is a correct SMR algorithm.

### 2016-01-01 paper/paper.tex
A new Isabelle formalization

Composable Generalized Consensus combines the ideas of the Abstract Framework \cite{GuerraouiETAL10Next700BftProtocols}, Generalized Conensus  \cite{Lamport05GeneralizeConsensus}, and Vertical Paxos \cite{LamportMalkhiZhou09VerticalPaxosPrimarybackupReplication} in a
unified abstraction.

Generalized Consensus is an agreement problem relaxing the ordering constraints
imposed on commuting commands and Generalized Paxos is an algorithm, similar
in structure to Fast Paxos, which takes advantage of the relaxed ordering
constraint to process commuting commands in two message delays, when three are
needed in the Classic Paxos algorithm.

>>>>

Composable Generalized Consensus combines the ideas of the Abstract Framework \cite{GuerraouiETAL10Next700BftProtocols}, Generalized Consensus  \cite{Lamport05GeneralizeConsensus}, and Vertical Paxos \cite{LamportMalkhiZhou09VerticalPaxosPrimarybackupReplication} in a
unified abstraction.

Generalized Consensus is an agreement problem relaxing the ordering constraints
imposed on commuting commands and Generalized Paxos \cite{Lamport05GeneralizeConsensus} is an algorithm, similar
in structure to Fast Paxos, which takes advantage of the relaxed ordering
constraint to process commuting commands in two message delays, when three are
needed in the Classic Paxos algorithm.

Generalized Paxos is also structured in a sequence of rounds, 
where each round maintains the agreement property of Generalized Consensus.
In the abstract presentation of Generalized Paxos, Lamport gives a generic and abstract algorithm (not a distributed algorithm, accesses directly the state of all acceptors and rounds) that a round must use to determine the values that are safe to be voted for in the round.
If all round refine this abstract specification, then the resulting algorithm implements Generalized Consensus. Therefore any set of rounds refining Lamport's abstract specification can be combined to form a correct generalized consensus algorithm.  
However, no explicit interface for combining rounds is given and specifying a type of round in isolation from the others would require assume-guarantee reasoning. In contrast, our formulation uses encapsulared rounds and does not require assume-guarantee reasoning.
